D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-05 ootavacuous.tex
volatile: Clarify preserved dependencies and prevented OOTA cycles
Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

These possibilities force the implementation to preserve the semantic
dependency from line~4 to line~5.
They can also prevent the formation of OOTA cycles local to the
implementation because such inteference means that the volatile loads
might be reading from something that the implementation knows nothing
about.

>>>>

These possibilities force the implementation to preserve the semantic
dependency from line~4 to line~5.
This preserved dependency helps prevent the formation of OOTA cycles
even in situations where there is no interference.\footnote{
	When there is interference, the definition of ``OOTA cycle''
	does not apply.}
